% -*- Mode: LaTeX; compile-command: "pdflatex cv.tex && open cv.pdf" -*-
\documentclass[a4paper,10pt]{article}
\usepackage[left=0cm, right=0.5cm, top=0cm, bottom=0cm]{geometry}
\usepackage{xcolor, fontawesome5, enumitem}
\usepackage[hidelinks]{hyperref}
\renewcommand{\familydefault}{\sfdefault} % Use sans-serif font
\pagestyle{empty} % No page numbers

% Define colour scheme
\definecolor{navy}{RGB}{15,30,132}         % Dark navy for headings
\definecolor{lightblue}{RGB}{100,149,237}  % Lighter blue for section accents
\definecolor{vlightblue}{RGB}{185,215,255} % Very lighter blue for softer accents
\definecolor{darkbg}{RGB}{30,30,30}        % Dark background for left column
\definecolor{headerbg}{RGB}{240,240,255}   % Skyblue for the header

\newcommand{\subskill}[1]{{\color{vlightblue} #1}}
\newcommand{\coreskills}[1]{\item Core Skills: #1}

% Set padding for colorbox
\setlength{\fboxsep}{10pt}

\begin{document}
\vbox to \paperheight{% Force all content into one box exactly as tall as the paper
\noindent
% Left Column: Contact, Skills, Education (approx. 27% width) with dark background
\begin{minipage}[t]{0.24\textwidth}
    \colorbox{darkbg}{%
    \begin{minipage}[t][\textheight]{\dimexpr\textwidth-10pt}
        \raggedright
        \vspace{0.5cm} % Adjusted top spacing

        {\color{lightblue} \LARGE \textbf{Oli Legat}}%
        \color{white} % Ensure all text here is white
        {\large\\[0.5em]Staff Software Engineer} \\[1em]
        \faIcon{map-marker-alt} London, UK \\
        \faIcon{envelope} \href{mailto:olivierleg@gmail.com}{olivierleg@gmail.com} \\
        \faIcon{phone} +44 1227 390 872 \\
        \faIcon{linkedin} \href{https://www.linkedin.com/in/olivier-legat}{linkedin.com/in/olivier-legat} \\
        \faIcon{github} \href{https://github.com/olegat}{github.com/olegat} \\

        \section*{\color{lightblue} Skills}

        \subskill{Leadership \& Management}
        \begin{itemize}[leftmargin=1em, nosep]
            \item Roadmap Planning
            \item XFN Team Collaboration
            \item Mentoring
            \item Hiring, onboarding \& retention
            \item DEI advocacy
            \item Inclusive a11y \& i18n design
            \item Performance reviews \& career progression planning
        \end{itemize}
        \vspace{0.5em}

        %% \subskill{Leadership \& Strategy}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Engineering strategy development \& execution
        %%     \item Technical vision \& roadmap planning
        %%     \item Cross-functional collaboration with product \& design teams
        %%     \item Architectural decision-making \& trade-offs
        %%     \item Budgeting \& resource allocation for engineering teams
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{People \& Team Management}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Leading, mentoring \& coaching engineering managers and ICs
        %%     \item Scaling engineering teams (hiring, onboarding, retention)
        %%     \item Performance reviews \& career progression planning
        %%     \item Fostering high-performance \& engineering culture
        %%     \item Diversity, Equity \& Inclusion (DEI) advocacy in tech teams
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{Software Engineering \& Architecture}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Scalable distributed systems design
        %%     \item High-performance computing \& low-latency optimization
        %%     \item Microservices, event-driven architecture \& service-oriented design
        %%     \item API design (REST, GraphQL, gRPC)
        %%     \item Cloud-native architecture (AWS, GCP, Azure)
        %%     \item Edge computing \& real-time data processing
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{Infrastructure \& DevOps}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Cloud platforms: AWS, GCP, Azure
        %%     \item Infrastructure as Code (Terraform, Pulumi, CloudFormation)
        %%     \item CI/CD pipelines \& automation (GitHub Actions, Jenkins, CircleCI)
        %%     \item Containerization \& orchestration (Docker, Kubernetes)
        %%     \item Observability \& monitoring (Prometheus, Grafana, OpenTelemetry)
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{Security \& Compliance}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Secure software development lifecycle (SSDLC)
        %%     \item Identity \& access management (OAuth, OIDC, SAML)
        %%     \item Threat modeling \& security audits
        %%     \item Compliance frameworks (ISO 27001, SOC 2, GDPR)
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{Product \& Business Alignment}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Bridging technical execution with business objectives
        %%     \item Working with stakeholders (C-suite, investors, board members)
        %%     \item Data-driven decision-making \& OKRs/KPIs
        %%     \item Technical due diligence for mergers \& acquisitions
        %% \end{itemize}
        %% \vspace{0.5em}

        %% \subskill{Open Source \& Community Engagement}
        %% \begin{itemize}[leftmargin=1em, nosep]
        %%     \item Contributions to major open-source projects (Mozilla Firefox, WineHQ, etc.)
        %%     \item Speaking at conferences \& technical writing
        %%     \item Developer advocacy \& community building
        %%     \item Running internal/external tech talks \& workshops
        %% \end{itemize}
        %% \vspace{0.5em}

        \subskill{Team Engagment}
        \begin{itemize}[leftmargin=1em, nosep]
            \item Fostering high-performance \& engineering culture
            \item Running tech talks \& workshops
        \end{itemize}
        \vspace{0.5em}

        \subskill{Software Engineering}
        \begin{itemize}[leftmargin=1em, nosep]
            \item C, C++, CMake
            \item Python, TypeScript, R
            \item Rust, Go
            \item Java, SQL, NoSQL
            \item Multi-threading, Networking
            \item Visual Studio, Xcode
            \item macOS, Windows, Linux, Android
        \end{itemize}
        \vspace{0.5em}

        \subskill{Spoken Languages}
        \begin{itemize}[leftmargin=1em, nosep]
            \item English, French (native)
            \item Spanish, Portuguese (fluent)
            \item Japanese, Dutch (limited)
        \end{itemize}

        \section*{\color{lightblue} Education}
        \textbf{MSc in Computer Science} \\
        University of East Anglia, 2012
        \vfill % Forces background to extend to the bottom
    \end{minipage}%
    }
\end{minipage}%
\hfill%
% Right Column: Name, Summary, Work Experience, Publications (approx. 73% width)
\begin{minipage}[t]{0.72\textwidth}
    % Header Section with light sky-blue background
    \hspace{-1.55em}
    \colorbox{headerbg}{%
    \begin{minipage}[t]{\dimexpr\textwidth + 0.65em}
        \vspace{0.5cm} % Adjusted top spacing
        \textit{Proficient engineering leader with 12+ years of professional experience in building high-performing teams and scalable technology solutions. Avid problem-solver with a passion for people management and developer relations. Former game developer specialised in low-level C/C++ programming, optimisation, reverse engineering and porting. Led over 10 published triple-A video games and engaged with large open source projects like Mozilla Firefox and WineHQ.}
        \vspace{0.3cm}
    \end{minipage}%
    }
    % Work Experience Section
    \section*{\color{navy} Work Experience}

    \textbf{AG Charts}, \textit{Staff Software Engineer} \hfill 2023 -- Present
    \begin{itemize}[leftmargin=1.5em, nosep]
        \coreskills{TypeScript, WAI-ARIA / WCAG Compliance}
        \item Developed and maintained a frontend charting library.
        \item Secured deals with new customers by delivering accessibility support.
        \item Engineered high-performance canvas rendering techniques, optimising interactive charting features.
        \item Led an initiative to eliminate technical debt, improving performance and long-term maintainability.
        \item Improved stability by expanding test coverage through automated image-based tests.
    \end{itemize}
    \vspace{0.5em}

    \textbf{Google Inc.}, \textit{Senior Technical Solutions Engineering Manager} \hfill 2018 -- 2023
    \begin{itemize}[leftmargin=1.5em, nosep]
        \coreskills{Management, DevRel, C++, C\#, Vulkan}
        \item Ensured the success of high-stakes multimillion-dollar partnerships with AAA game studios.
        \item Received Spot Bonus from Google VP for outstanding technical contributions.
        \item Travelled onsite to partners to troubleshoot \& pitch upcoming platform features.
        \item Attended developer conferences such as GDC to foster business relations.
        \item Contributed to the development of a Visual Studio Extension and C/C++ Developer SDK.
        \item Scaled-up workforce by interviewing candidates and onboarding new hires.
        \item Leveraged my proficiency in Spanish to aid Google's DEI hiring initiative.
        \item Mentored \& trained team members by presenting internal Tech Talks.
        \item Spearheaded the development of binary translation technology, enabling unmodified Windows games to run efficiently on Cloud-native Linux VMs.
        \item Managed technical teams working on developer tools, boosting the team's productivity and job satisfaction.
    \end{itemize}
    \vspace{0.5em}

    \textbf{Garrison Technology (now part of Everfox)}, \textit{Software Engineer} \hfill 2017 -- 2018
    \begin{itemize}[leftmargin=1.5em, nosep]
        \coreskills{C++, C\#, Qt, Android}
        \item Customised Mozilla Firefox for in-house endpoint security technology.
        \item Migrated build system to CMake, drastically improving build times and developer efficiency.
        \item Developed a cross-platform video client desktop application for  Windows, Linux, and macOS.
        \item Promptly implemented feature requests from sales teams to acquire \& retain clients.
    \end{itemize}
    \vspace{0.5em}

    \textbf{Feral Interactive Ltd.}, \textit{Game Developer} \hfill 2012 -- 2017
    \begin{itemize}[leftmargin=1.5em, nosep]
        \coreskills{C, C++, Perl, Python}
        \item Ported high-profile Windows video games to macOS, Linux, and Android
        \item Adapted DirectX APIs to Metal, OpenGL, and Vulkan.
        \item Optimised performance and memory management of games.
        \item Designed and integrated portable networking client library.
        \item Led a team of up to 10 engineers, mentoring developers and ensuring successful project deliveries.
        \item Overhauled and re-architected a legacy I/O system, significantly reducing recurring bugs and improving long-term stability.
    \end{itemize}

    \section*{\color{navy} Publications}
    \textbf{OpenABM-Covid19—An agent-based model for non-pharmaceutical interventions against COVID-19 including contact tracing}\\
    Institutions: \textit{Google Research}, \textit{Oxford University} \hfill 2020 -- 2021\\[1.0em]
    Co-authored COVID-19 research by developing R bindings for epidemiologists to use in their viral transmission simulator. Research findings influenced UK policies and healthcare services.\\
    \href{https://doi.org/10.1371/journal.pcbi.1009146}{https://doi.org/10.1371/journal.pcbi.1009146}
\end{minipage}%
\vfill % Ensure the box stretches to the bottom
}% End of vbox to \paperheight
\end{document}
